Pillar 2 - Topic Modeling

### 2019-03-22 Pillar 2 - Topic Modeling.Rmd
minor change

         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast),

@@

```
## Saving files for APP
```{r app files}
# save(app_topic_model, course_all, course_following_semester,
#      file = "App/Recommender System/data_topic_models.RDATA")
```
# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

@@

rm(a,b #,test)
```
This part is not adapted
```{r LDA visualize, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

>>>>

         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast), #my_control

@@

```{r adding convenience vectors}
app_topic_model <- app_topic_model %>%
  mutate(`All Courses`     = course_all,
         `Sample semester` = course_following_semester)

#rm(course_all, course_following_semester)
```
## Saving files for APP
```{r app files}
# save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
```
# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

@@

test <- test_topic_model %>%
  mutate(preparedBeta = pmap(list(Beta), .f = prepare_data_LDA_beta),
         preparededGamma = pmap(list(Gamma), .f = prepare_data_LDA_gamma)
         )
test[["preparedBeta"]]
rm(a,b #,test
   )
```
This part is not adapted
```{r LDA visualize, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){
